---
title: "Working Capital Forecasting Dashboard"
output: 
  flexdashboard::flex_dashboard
date: '2022-07-29'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r, packages, results="hide", , message = FALSE}
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)

library(patchwork)
library(GGally)
library(knitr)
library(printr)
library(DT)
```
```{r, import and clean data, results="hide", , message = FALSE}
google_gl <- read_csv("C:\\Users\\AxelTorbenson\\OneDrive - eCapital Advisors, LLC\\Documents\\templates\\CapitalForecasting\\Data\\goog_gl.csv")

gl <- google_gl %>%
  select(
    # date and totals
    fiscalDateEnding,
    totalCurrentAssets,
    totalCurrentLiabilities,
    # assets
    inventory,
    cashAndCashEquivalentsAtCarryingValue, 
    currentNetReceivables,
    shortTermInvestments,
    otherCurrentAssets,
    # liabilities
    shortTermDebt,
    currentAccountsPayable,
    otherCurrentLiabilities) %>%
  mutate(workingCapital = totalCurrentAssets - totalCurrentLiabilities,
         otherCurrentAssets = totalCurrentAssets
         - inventory
         - cashAndCashEquivalentsAtCarryingValue
         - currentNetReceivables 
         - shortTermInvestments,
         # otherCurrentLiabilities includes taxes, deferred revenue, capital lease obligations, and other
         otherCurrentLiabilities = totalCurrentLiabilities
         - shortTermDebt 
         - currentAccountsPayable,
         # NA is equivalent to 0
         across(where(is.numeric), ~replace(., is.na(.), 0)),
         # Make data in millions
         across(c(2:12), .fns = ~./1000000),
         # Liabilities are negative
         across(c("shortTermDebt", "currentAccountsPayable", "otherCurrentLiabilities"), .fns = ~. * -1)) %>% 
  select(-workingCapital, -totalCurrentAssets, -totalCurrentLiabilities) %>% 
  pivot_longer(!fiscalDateEnding, values_to = "dollars") %>%
  group_by(name) %>%
  mutate(accountType = case_when(
    name %in% c(
      "inventory",
      "cashAndCashEquivalentsAtCarryingValue",
      "currentNetReceivables",
      "shortTermInvestments",
      "otherCurrentAssets"
    ) ~ "asset",
    name %in% c(
      "shortTermDebt",
      "currentAccountsPayable",
      "otherCurrentLiabilities"
    ) ~ "liability")
  )

df <- gl %>%
  mutate(fiscalDateEnding = yearmonth(fiscalDateEnding)) %>%
  as_tsibble(key = dollars, index = fiscalDateEnding) %>%
  aggregate_key((accountType / name), dollars = sum(dollars)) 

ind_models <- df %>% 
  # withholding 5 quarters of data (training)
  filter(year(fiscalDateEnding) <= 2020) %>%
  # AICc is better for short time series
  model(arima = ARIMA(dollars, ic = "aicc"),
        ets = ETS(dollars, ic = "aicc"),
        naive = NAIVE(dollars ~ drift()))

refit_comb <- ind_models %>%
  refit(df) %>%
  mutate(comb = (arima + ets + naive) / 3) %>%
  reconcile(mint_comb = min_trace(comb, method = "mint_shrink")) %>% 
  select(accountType, name, mint_comb)

# refits forecast and uses newest data
refit_forecast <- refit_comb %>% 
  forecast(h = 5) %>% 
  hilo(95) %>%
  as_tibble() %>%
  select(fiscalDateEnding, accountType, name, .mean, '95%') %>%
  rename(dollars = .mean) %>%
  rename(conf_int = '95%') %>%
  unpack_hilo(conf_int) %>% 
  mutate(type = "forecast")

df_final <- df %>%
  mutate(conf_int_lower = NA,
         conf_int_upper = NA,
         type = "actual")

full_df = union_all(refit_forecast, df_final)
```

# Working Capital Forecast

## Column {.tabset .tabset-fade}

### Stacked area assets and Liabilities

```{r, stacked area charts}
sa_assets <- gl %>%
  filter(
    name %in% c(
      "fiscalDateEnding",
      "inventory",
      "cashAndCashEquivalentsAtCarryingValue",
      "currentNetReceivables",
      "shortTermInvestments",
      "otherCurrentAssets"
    )
  ) %>%
  mutate(name=replace(name, name=="cashAndCashEquivalentsAtCarryingValue", "cash")) %>% 
  ggplot(aes(x = fiscalDateEnding, y = dollars, fill = name)) +
  geom_area() +
  labs(title = "Assets") +
  scale_fill_brewer(palette = "Pastel1")


sa_liabilities <- gl %>%
  filter(
    name %in% c(
      "fiscalDateEnding",
      "shortTermDebt",
      "currentAccountsPayable",
      "otherCurrentLiabilities"
    )
  ) %>%
  mutate(dollars = abs(dollars)) %>%
           ggplot(aes(x = fiscalDateEnding, y = dollars, fill = name)) +
           geom_area() + 
           labs(title = "Liabilities") +
           scale_fill_brewer(palette = "Pastel1")

sa_assets / sa_liabilities
```

## Column {.tabset .tabset-fade}

### Working Capital Forecasting

```{r, working capital forecast}
refit_comb %>%
  forecast(h=5) %>% 
  filter(is_aggregated(name), is_aggregated(accountType)) %>%
  filter(.model == "mint_comb") %>% 
  autoplot(df) +
  facet_wrap(vars(name), scales = "free_y") +
  labs(y = "Dollars (millions)", x = "Date", title = "Working Capital forecast") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 160000), labels = function(x) format(x, scientific = FALSE)) 
```

### Working Capital Simulation

```{r, working capital simulation}
simulation <- generate(refit_comb, h = 5, times = 10) %>%
  filter(is_aggregated(name), is_aggregated(accountType)) %>% 
  filter(.model == 'mint_comb')
df %>%
  filter(is_aggregated(name), is_aggregated(accountType)) %>%
  autoplot(dollars) + 
  autolayer(simulation, .vars = .sim) +
  geom_line() +
  theme(legend.position = "none") +
  ggtitle("Working Capital Simulation") +
  labs(y = "Dollars (millions)", x = "Date") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 160000), labels = function(x) format(x, scientific = FALSE))
```

# GL components forecast

## Column {.tabset .tabset-fade}

### Assets

```{r, assets}
refit_comb %>%
  forecast(h=5) %>% 
  filter(is_aggregated(name), accountType == "asset") %>%
  filter(.model == "mint_comb") %>% 
  autoplot(df) +
  facet_wrap(vars(name), scales = "free_y") +
  labs(y = "Dollars (millions)", x = "Date", title = "Assets Forecast")
```

### Asset Components

```{r, assets components}
five_period_forecast <- refit_comb %>%
  forecast(h=5)
components_plot <- function(gl_component, account_type) {
  five_period_forecast %>% 
    filter(name == gl_component, accountType == account_type) %>%
    filter(.model == "mint_comb") %>% 
    autoplot(df) +
    facet_wrap(vars(name), scales = "free_y") +
    labs(y = "", x = "") +
    theme(legend.position = "none")
}

(components_plot("cashAndCashEquivalentsAtCarryingValue", "asset") + components_plot("currentNetReceivables", "asset")) /
  (components_plot("inventory", "asset") + components_plot("otherCurrentAssets", "asset")) /
  components_plot("shortTermInvestments", "asset")
```

## Column {.tabset .tabset-fade}

### Liabilities

```{r, liabilities}
refit_comb %>%
  forecast(h=5) %>% 
  filter(is_aggregated(name), accountType == "liability") %>%
  filter(.model == "mint_comb") %>% 
  autoplot(df) +
  facet_wrap(vars(name), scales = "free_y") +
  labs(y = "Dollars (millions)", x = "Date", title = "Liabilities Forecast")
```

### Liabilities Components

```{r, liabilities components}
(components_plot("currentAccountsPayable", "liability") + components_plot("shortTermDebt", "liability")) /
  components_plot("otherCurrentLiabilities", "liability")
```

# Accuracy and hierarchy

## Column

### Accuracy

```{r, accuracy}
# This combination model is just to get the error of the model
comb_forecast_accuracy <- ind_models %>%
  mutate(comb = (arima + ets + naive) / 3) %>%
  reconcile(mint_comb = min_trace(comb, method = "mint_shrink")) %>% 
  forecast(h = 5) %>% 
  filter(.model == "mint_comb") %>% 
  # MAPE is infinity when a series has 0 in it
  accuracy(data = df, measures = c(mape = MAPE, mae = MAE, mase = MASE)) %>% 
  select(accountType, name, mape, mae, mase) %>% 
  mutate(mape = round(mape, 3), mae = round(mae, 3), mase = round(mase, 3))

datatable(comb_forecast_accuracy %>% 
  mutate(accountType = as.character(accountType), name = as.character(name)),
  class = 'cell-border stripe')
```

## Column

### Hierarchical Structure

```{r, hierarchy}
library(ggraph)
library(igraph)
  
# create a data frame
data <- data.frame(
  level1="Working Capital",
  level2=c(rep(" Current Assets", 5), rep("Current Liabilities", 3)),
  level3=c("Inventory",
      "Net Receivables",
      "Cash",
      "Investments",
      "other",
      "Debt",
      "Acc Payable",
      "other")
)
  
# transform it to a edge list!
edges_level1_2 <- data %>% select(
  level1, level2) %>% unique %>% rename(
  from=level1, to=level2)
 
edges_level2_3 <- data %>% select(
  level2, level3) %>% unique %>% rename(
  from=level2, to=level3)
 
edge_list=rbind(edges_level1_2, edges_level2_3)

# Now we can plot that
graph_Data <- graph_from_data_frame( edge_list )
suppressMessages(ggraph(graph_Data, layout = 'dendrogram') +
  geom_edge_diagonal(color = "azure4") +
  geom_node_text(aes(label=name), color="cornflowerblue") +
  theme_void() +
  theme(legend.position = "none"))
```

# Data

## Column

### Data

```{r, table}
table_df <- full_df %>% 
  mutate(accountType = as.character(accountType), 
         name = as.character(name),
         fiscalDateEnding = as.character(fiscalDateEnding)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(name=replace(name, name=="cashAndCashEquivalentsAtCarryingValue", "cash"))


datatable(
  table_df,
  class = 'cell-border stripe',
  fillContainer = TRUE
)
```
