---
title: "Working Capital Forecasting Dashboard"
output: 
  flexdashboard::flex_dashboard
date: '2022-07-29'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, packages, results="hide", , message = FALSE}
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)

library(patchwork)
library(GGally)
library(knitr)
library(printr)
library(DT)
```

```{r, import clean and model, results="hide", , message = FALSE}
google_gl <- read_csv("C:\\Users\\AxelTorbenson\\OneDrive - eCapital Advisors, LLC\\Documents\\templates\\CapitalForecasting\\Data\\gl_google.csv")

gl <- google_gl %>%
  select(
    # date and totals
    fiscalDateEnding,
    totalCurrentAssets,
    totalCurrentLiabilities,
    # assets
    inventory,
    cashAndCashEquivalentsAtCarryingValue, 
    currentNetReceivables,
    shortTermInvestments,
    otherCurrentAssets,
    # liabilities
    shortTermDebt,
    currentAccountsPayable,
    otherCurrentLiabilities) %>%
  mutate(workingCapital = totalCurrentAssets - totalCurrentLiabilities,
         otherCurrentAssets = totalCurrentAssets
         - inventory
         - cashAndCashEquivalentsAtCarryingValue
         - currentNetReceivables 
         - shortTermInvestments,
         # otherCurrentLiabilities includes taxes, deferred revenue, capital lease obligations, and other
         otherCurrentLiabilities = totalCurrentLiabilities
         - shortTermDebt 
         - currentAccountsPayable,
         # NA is equivalent to 0
         across(where(is.numeric), ~replace(., is.na(.), 0)),
         # Make data in millions
         across(c(2:12), .fns = ~./1000000),
         # Liabilities are negative
         across(c("shortTermDebt", "currentAccountsPayable", "otherCurrentLiabilities"), .fns = ~. * -1)) %>% 
  select(-workingCapital, -totalCurrentAssets, -totalCurrentLiabilities) %>% 
  pivot_longer(!fiscalDateEnding, values_to = "dollars") %>%
  group_by(name) %>%
  mutate(accountType = case_when(
    name %in% c(
      "inventory",
      "cashAndCashEquivalentsAtCarryingValue",
      "currentNetReceivables",
      "shortTermInvestments",
      "otherCurrentAssets"
    ) ~ "asset",
    name %in% c(
      "shortTermDebt",
      "currentAccountsPayable",
      "otherCurrentLiabilities"
    ) ~ "liability")
  )

df <- gl %>%
  mutate(fiscalDateEnding = yearmonth(fiscalDateEnding)) %>%
  as_tsibble(key = dollars, index = fiscalDateEnding) %>%
  aggregate_key((accountType / name), dollars = sum(dollars)) 

ind_models <- df %>% 
  # withholding 5 quarters of data (training)
  filter(year(fiscalDateEnding) <= 2020) %>%
  # AICc is better for short time series
  model(arima = ARIMA(dollars, ic = "aicc"),
        ets = ETS(dollars, ic = "aicc"),
        naive = NAIVE(dollars ~ drift()))

refit_comb <- ind_models %>%
  refit(df) %>%
  mutate(comb = (arima + ets + naive) / 3) %>%
  reconcile(mint_comb = min_trace(comb, method = "mint_shrink")) %>% 
  select(accountType, name, mint_comb)

# refits forecast and uses newest data
refit_forecast <- refit_comb %>% 
  forecast(h = 5) %>% 
  hilo(95) %>%
  as_tibble() %>%
  select(fiscalDateEnding, accountType, name, .mean, '95%') %>%
  rename(dollars = .mean) %>%
  rename(conf_int = '95%') %>%
  unpack_hilo(conf_int) %>% 
  mutate(type = "forecast")

df_final <- df %>%
  mutate(conf_int_lower = NA,
         conf_int_upper = NA,
         type = "actual")

full_df = union_all(refit_forecast, df_final)
```

# Working Capital Forecast

## Column {.tabset .tabset-fade}

### Stacked area assets and Liabilities

```{r, stacked area charts}
library(highcharter)
library(htmltools)

# Might need to format these like patchwork:: normally would.
# https://www.tmbish.me/lab/highcharter-cookbook/#forecast
hw_grid(gl %>%
  filter(
    name %in% c(
      "fiscalDateEnding",
      "inventory",
      "cashAndCashEquivalentsAtCarryingValue",
      "currentNetReceivables",
      "shortTermInvestments",
      "otherCurrentAssets"
    )
  ) %>%
  arrange(fiscalDateEnding) %>% 
  hchart(
    "area",
    hcaes(fiscalDateEnding, dollars, group = name),
    stacking = "normal",
    marker = FALSE
  ),
gl %>%
  filter(
    name %in% c(
      "fiscalDateEnding",
      "shortTermDebt",
      "currentAccountsPayable",
      "otherCurrentLiabilities"
    )) %>% 
  arrange(fiscalDateEnding) %>% 
  mutate(dollars = abs(dollars)) %>%
  hchart(
    "area",
    hcaes(fiscalDateEnding, dollars, group = name),
    stacking = "normal",
    marker = FALSE
  ), ncol = 1) %>% browsable()
```

## Column {.tabset .tabset-fade}

### Working Capital Forecasting

```{r, working capital forecast}
library(dygraphs)
library(tsbox)

predictions <- full_df %>% 
  filter(is_aggregated(name), is_aggregated(accountType), type == "forecast") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars, conf_int_lower, conf_int_upper) %>% 
  as_tsibble() %>% 
  ts_xts()

actuals <- full_df %>% 
  filter(is_aggregated(name), is_aggregated(accountType), type == "actual") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars) %>% 
  as_tsibble() %>% 
  ts_xts()

both <- cbind(actuals, predictions)

dygraph(both, main = "Working Capital Forecast") %>%
  dySeries("dollars", label = "Actual", color = "gold", strokeWidth = 1.5) %>%
  dySeries(c("conf_int_lower", "dollars.1", "conf_int_upper"), label = "Predicted", color = "blue", strokeWidth = 1.5) %>% 
  dyAxis('y', valueRange = c(0, 160000)) %>% 
  dyOptions(gridLineWidth = 0.05)
```

### Working Capital Simulation

```{r, working capital simulation}
simulation <- generate(refit_comb, h = 5, times = 10) %>%
  filter(is_aggregated(name), is_aggregated(accountType)) %>% 
  filter(.model == 'mint_comb')
df %>%
  filter(is_aggregated(name), is_aggregated(accountType)) %>%
  autoplot(dollars) + 
  autolayer(simulation, .vars = .sim) +
  geom_line() +
  ggtitle("Working Capital Simulation") +
  labs(y = "Dollars (millions)", x = "Date") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 160000), labels = function(x) format(x, scientific = FALSE)) + 
  theme_minimal() + 
  theme(legend.position = "none")
```

# GL components forecast

## Column {.tabset .tabset-fade}

### Assets

```{r, assets}
predictions <- full_df %>% 
  filter(is_aggregated(name), accountType == "asset", type == "forecast") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars, conf_int_lower, conf_int_upper) %>% 
  as_tsibble() %>% 
  ts_xts()

actuals <- full_df %>% 
  filter(is_aggregated(name), accountType == "asset", type == "actual") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars) %>% 
  as_tsibble() %>% 
  ts_xts()

both <- cbind(actuals, predictions)

dygraph(both, main = "Current Assets Forecast") %>%
  dySeries("dollars", label = "Actual", color = "gold", strokeWidth = 1.5) %>%
  dySeries(c("conf_int_lower", "dollars.1", "conf_int_upper"), label = "Predicted", color = "blue", strokeWidth = 1.5) %>% 
  dyOptions(gridLineWidth = 0.05)
```

### Asset Components

```{r, assets components}
five_period_forecast <- refit_comb %>%
  forecast(h=5)
components_plot <- function(gl_component, account_type) {
  five_period_forecast %>% 
    filter(name == gl_component, accountType == account_type) %>%
    filter(.model == "mint_comb") %>% 
    autoplot(df) +
    facet_wrap(vars(name), scales = "free_y") +
    labs(y = "", x = "") +
    theme_minimal() +
    theme(legend.position = "none")
}

(components_plot("cashAndCashEquivalentsAtCarryingValue", "asset") + components_plot("currentNetReceivables", "asset")) /
  (components_plot("inventory", "asset") + components_plot("otherCurrentAssets", "asset")) /
  components_plot("shortTermInvestments", "asset")
```

## Column {.tabset .tabset-fade}

### Liabilities

```{r, liabilities}
predictions <- full_df %>% 
  filter(is_aggregated(name), accountType == "liability", type == "forecast") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars, conf_int_lower, conf_int_upper) %>% 
  as_tsibble() %>% 
  ts_xts()

actuals <- full_df %>% 
  filter(is_aggregated(name), accountType == "liability", type == "actual") %>% 
  mutate(time = fiscalDateEnding) %>% 
  select(time, dollars) %>% 
  as_tsibble() %>% 
  ts_xts()

both <- cbind(actuals, predictions)

dygraph(both, main = "Current Liabilities Forecast") %>%
  dySeries("dollars", label = "Actual", color = "gold", strokeWidth = 1.5) %>%
  dySeries(c("conf_int_lower", "dollars.1", "conf_int_upper"), label = "Predicted", color = "blue", strokeWidth = 1.5) %>% 
  dyOptions(gridLineWidth = 0.05)
```

### Liabilities Components

```{r, liabilities components}
(components_plot("currentAccountsPayable", "liability") + components_plot("shortTermDebt", "liability")) /
  components_plot("otherCurrentLiabilities", "liability")
```

# Accuracy and hierarchy

## Column

### Accuracy

```{r, accuracy}
# This combination model is just to get the error of the model
comb_forecast_accuracy <- ind_models %>%
  mutate(comb = (arima + ets + naive) / 3) %>%
  reconcile(mint_comb = min_trace(comb, method = "mint_shrink")) %>% 
  forecast(h = 5) %>% 
  filter(.model == "mint_comb") %>% 
  # MAPE is infinity when a series has 0 in it
  accuracy(data = df, measures = c(mape = MAPE, mae = MAE, mase = MASE)) %>% 
  select(accountType, name, mape, mae, mase) %>% 
  mutate(mape = round(mape, 3), mae = round(mae, 3), mase = round(mase, 3))

datatable(comb_forecast_accuracy %>% 
  mutate(accountType = as.character(accountType), name = as.character(name)),
  class = 'cell-border stripe')
```

## Column

### Hierarchical Structure

```{r, hierarchy}
library(collapsibleTree)

# Add "current"
# Should change the colors (maybe make a gradient?) and the names of each asset to look nicer
# http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf
# https://adeelk93.github.io/collapsibleTree/
# https://github.com/AdeelK93/collapsibleTree
hierarchy <- data.frame(
  accountType = c(
    NA,
    "Working Capital",
    "Working Capital",
    "Assets",
    "Assets",
    "Assets",
    "Assets",
    "Assets",
    "Liabilities",
    "Liabilities",
    "Liabilities"
  ),
  accountName = c(
    "Working Capital",
    "Assets",
    "Liabilities",
    "Inventory",
    "Net Receivables",
    "Cash",
    "Investments",
    "other",
    "Debt",
    "Acc Payable",
    "other"
  ),
  Category = c(
    "Working Capital",
    "Asset",
    "Liability",
    "Asset",
    "Asset",
    "Asset",
    "Asset",
    "Asset",
    "Liability",
    "Liability",
    "Liability"
  ),
  color = c(
    "cornflowerblue",
    "gold",
    "gold",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise",
    "darkturquoise"
  )
)

collapsibleTreeNetwork(hierarchy, attribute = "Category",
                       collapsed = FALSE,
                       fill = "color")
```


# Data

## Column

### Data

```{r, table}
table_df <- full_df %>% 
  mutate(accountType = as.character(accountType), 
         name = as.character(name),
         fiscalDateEnding = as.character(fiscalDateEnding)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(name=replace(name, name=="cashAndCashEquivalentsAtCarryingValue", "cash"))


datatable(
  table_df,
  class = 'cell-border stripe',
  fillContainer = TRUE
  )
```
